XP-C Deamination Anchored Excision Site Figure Generation

### 2022-06-15 R/XP-CDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update XP-C notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 10
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

expansionOffset = 10
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 30
